\documentclass[11pt]{katz_resume}
\pagenumbering{\gobble}

\author{Harrison J Katz}
\email{hjkatz03@gmail.com}
\streetaddress{950 Marietta St NW Apt 5301}
\citystatezip{Atlanta, GA 30318}
\phone{706.801.5289}
\webpage{www.linkedin.com/in/harrisonkatz}

\begin{document}
\maketitle

\section{Experience}
\begin{jobs}
    \job{Special Projects Developer}{Nead Werx, Inc.}{Atlanta, GA}{May 2014}{Present}{Developer of special projects mainly related to Linux Systems Administration and IT.}
    \job{Junior Mobile Apps Developer}{Nead Werx, Inc.}{Atlanta, GA}{May 2012}{May 2014}{Developer for the Mobile App Team designing mobile applications for Android and the Web in collaboration with a team. (Co-op for 3 semesters and Part-Time for 1)}
    \job{Classroom Support}{Georgia Institute of Technology}{Atlanta, GA}{Nov 2011}{Aug 2013}{Student classroom support assistant in charge of checking rooms to ensure AV equipment works, cleaning and repairing projectors, and helping to solve issues with the AV systems in place.}
    \experience{Professionally Proficient Skills}{
        \begin{skills}{6}
            \item[] Android
            \item[] Android Studio
            \item[] CentOS
            \item[] Git
            \item[] HTML
            \item[] Intellij
            \item[] Java
            \item[] JavaScript
            \item[] JSON
            \item[] Kotlin
            \item[] LaTeX
            \item[] Perl
            \item[] PHP
            \item[] SQL
            \item[] SVN
            \item[] Ubuntu
            \item[] Vim
            \item[] XML
        \end{skills}
    }
\end{jobs}

\section{Education}
\begin{schools}
    \school{Georgia Institute of Technology}{3.65}{Aug 2011}{May 2015}{Bachelors of Computer Science}{Atlanta, GA}
    \school{University of Georgia Dual Enrollment}{3.5}{Aug 2010}{May 2011}{Completed Coursework in CS}{Athens, GA}
\end{schools}


\section{Projects \& Research}
\begin{projects}
    \project{Donation Tracker}{}{Georgia Tech Senior Design}{Dec 2014}{My senior design project for Georgia Tech involved creating a donation tracking and management website for non-profit organizations. This project had me coordinating and leading a team of 5 students in the development of this website. This project made extensive use of HTML, PHP, Javascript, PostgreSQL and the project tracking site JIRA.}
    \project{Nead Money}{http://www.neadmoney.com}{Nead Werx, Inc.}{Jan 2013}{Nead Money is an Android application made under the direction and collaboration with a team leader to allow Freshbooks' users to edit and view their financial account. This project involved multiple API integration including Freshbook's and Twitter's.}
    \project{Critiquestr}{http://www.critiquestr.com}{Nead Werx, Inc.}{Jul 2012}{This is a critiquing app for wine and beer festivals created for the Georgia Aquarium's ``Red, White \& Brew'' beer festival. It is written in HTML with Jquery, Javascript, and PHP. This project involved the cooperation and coordination between 3 different areas of development: Back-end, Middleware, and Front-end.}
    \project{Eagle Scout Project}{}{Troop 537\ in Bogart, GA}{Jun 2010}{Developed and facilitated a 100+ hours project to improve the running trails at North Oconee High School (NOHS). This project involved me leading over 70 people during multiple work days. The project included measuring, mapping, labeling, and marking the trails, as well as installing a Message Center (with a place for announcements and a large map with the mileage and trails marked and named) at the main entrance.}
    \project{AmigoBot Research}{http://www.cs.uga.edu/directory/prashant-doshi}{UGA Young DAWGS}{Dec 2010}{In collaboration with Dr. Prashant Doshi of the University of Georgia, I researched various localization strategies and map planning algorithms for the AmigoBot platform utilizing the C++ and Java languages.}
\end{projects}

\section{Honors \& Awards}
\begin{awards}
    \award{Eagle Scout Award}{BSA Highest Honor}{Jul 2010}
    \award{GA Tech Dean's List}{GPA 3.65 Overall}{Dec 2011 \-- Present}
    \award{Senior Patrol Leader}{BSA Leadership Role}{Jun 2009 \-- Nov 2009}
    \award{Moore's Ford Scholarship}{}{May 2011}
\end{awards}


\end{document}
